---
title: "Lab 7"
author: 'Roman Bond, Dan Grogan, Iglika Hadjiyska'
date: '4/13/18'
output:
  pdf_document: default
  html_document:
    fig_height: 4
    fig_width: 6
---

**Author:** Dan Grogan

**Discussants:** Roman Bond, Iglika Hadjiyska

* * *

**Load data:**



```{r echo=FALSE}
library("ISLR")
?Weekly
head(Weekly)
attach(Weekly)
```

* * *

#### 1:

```{r}
summary(Weekly)

plot(Weekly)

plot(Volume~Year)
```

There doesn't appear to be a strong correlation between many of the variables in the data set, however Year and Volume seem to have a correlation.


#### 2:

```{r}
mod1 = glm(Direction ~ Lag1 + Lag2 + Lag3 + Lag4 + Lag5 + Volume, family = binomial)
summary(mod1)
```

Lag 2 is statistically significant because it has a p-value of 0.03 which is less than 0.05.


#### 3: 

```{r}
train = Weekly[which(Year <= 2008),]
test = Weekly[which(!(Year <= 2008)),]
dir2018 = Weekly$Direction[!(Year<= 2008)]

probs1=predict(mod1,test,type="response")
dim(test)
pred1=rep("Down",104)
pred1[probs1>.5]="Up"
table(pred1,dir2018)
prate1 = (17+48) / 104
prate1
```

#### 4:

```{r}
mod2 = glm(Direction ~ Lag2, family = binomial)

probs2=predict(mod2,test,type="response")
pred2=rep("Down",104)
pred2[probs2>.5]="Up"
table(pred2,dir2018)
prate2 = (9 + 56) / 104
prate2

mod3 = glm(Direction ~ Lag1 + Lag2 + Volume, family = binomial)

probs3=predict(mod3,test,type="response")
pred3=rep("Down",104)
pred3[probs3>.5]="Up"
table(pred3,dir2018)
prate3 = (11 + 52) / 104
prate3

```


```{r}
head(Auto)
```

#### 5:

```{r}
Auto$mpg01=ifelse(Auto$mpg>=median(Auto$mpg),1,0) 
attach(Auto)
```

#### 6:

```{r}
plot(Auto)
plot(mpg01~displacement)
plot(mpg01~horsepower)
plot(mpg01~weight)
```

Based off of the above plots, it seems that displacement, horsepower and weight may be useful predictors for mpg01.

#### 7:

```{r}
condition = (year<=80)
Auto.train = Auto[condition,] #The training data set will be composed of cars made in the year 1980 or earlier
Auto.test = Auto[!condition,] # The test data set will be composed of cars made later than 1980
```


#### 8:

```{r}
mod4 = glm(mpg01 ~ displacement + horsepower + weight, data = Auto.train, family = binomial)
prob4 = predict(mod4, Auto.test, type = "response")
Auto.d = rep(0,nrow(Auto.test))
Auto.d[prob4 >=.5] = 1
table(Auto.d,Auto.test$mpg01)
Auto.prate = (4 + 46)/58
Auto.prate
```